% Remove header text
\markboth{}{}

\begin{thebibliography}{99}
\addcontentsline{toc}{section}{References}

    % Remove header text (I don't know why I have to do this twice)
    \markboth{}{}

    \bibitem{textbook}
        A. Silberschatz, P. B. Galvin, G. Gagne,
        \textit{Operating System Concepts}, 10th ed.,
        John Wiley and Sons, Inc., 2018.

    \bibitem{ingelhag}
        J. Ingelhag,
        ``How to choose an operating system for an embedded system'',
        \"Orebro Universitet, 2023.
        Accessed February 9, 2024.
        [Online].
        Available: \urllink{https://www.diva-portal.org/smash/get/diva2:1773441/FULLTEXT01.pdf}.

    \bibitem{whatislinux}
        The Linux Foundation,
        ``What is Linux?,''
        \textit{The Linux Foundation}.
        Accessed February 7, 2024.
        [Online].
        Available: \urllink{https://www.linux.com/what-is-linux/}.

    \bibitem{rtos-overview}
        W. Cede\~no, P.A. Laplante.
        ``An Overview of Real-Time Operating Systems,''
        JALA: Journal of the Association for Laboratory Automation, 2007, ch. 12, sec. 1, pp. 40-45.
        Accessed February 7, 2024.
        [Online].
        Available: \urllink{https://doi.org/10.1016/j.jala.2006.10.016}.

    \bibitem{laplante}
        P. A. Laplante,
        ``Real-Time Systems Design and Analysis,'' 3rd ed.,
        Hoboken, NJ, Wiley, 2004, p. 505.
        Accessed February 7, 2024.
        [Online].
        Available: \urllink{https://doi.org/10.1002/0471648299.fmatter}.

    \bibitem{stallman}
        R. Stallman,
        ``Linux and the GNU System,''
        \textit{Free Software Foundation}.
        Accessed February 9, 2024.
        [Online].
        Available: \urllink{https://www.gnu.org/gnu/linux-and-gnu.en.html}.

    \bibitem{comparative-os}
        A. Adekotujo, A. Odumabo, A. Adedokun, O. Aiyeniko,
        ``A Comparative Study of Operating Systems: Case of Windows, UNIX, Linux, Mac, Android and iOS,''
        International Journal of Computer Applications, 2020.
        Accessed February 10, 2024.
        [Online].
        Available: \href{https://www.researchgate.net/profile/Adedoyin-Odumabo/publication/343013056\_A\_Comparative\_Study\_of\_Operating\_Systems\_Case\_of\_Windows\_UNIX\_Linux\_Mac\_Android\_and\_iOS/links/61f2b50a9a753545e2fe8300/A-Comparative-Study-of-Operating-Systems-Case-of-Windows-UNIX-Linux-Mac-Android-and-iOS.pdf}{https://www.researchgate.net/profile/Adedoyin-Odumabo/publication/343013056\_A\_Comparative\_Study\_of\_Operating\_Systems\_Cas e\_of\_Windows\_UNIX\_Linux\_Mac\_Android\_and\_iOS/links/61f2b50a9a753545e2fe8300 /A-Comparative-Study-of-Operating-Systems-Case-of-Windows-UNIX-Linux-Mac-A ndroid-and-iOS.pdf}.

    \bibitem{grandview}
        Grand View Research,
        ``Server Operating System Market Size, Share \& Trends Analysis Report By Operating System (Windows, Linux), By Virtualization (Virtual Machine, Physical), By Deployment, By Region, And Segment Forecasts, 2022 - 2030,''
        \textit{Grand View Research}, 2020.
        Accessed February 10, 2024.
        [Online].
        Available: \urllink{https://www.grandviewresearch.com/industry-analysis/server-operating-system-market-report}.

    \bibitem{linux-public-cloud}
        The Linux Foundation,
        ``Linux Runs All of the World's Fastest Supercomputers,''
        \textit{The Linux Foundation}, November 20, 2017.
        Accessed February 10, 2024.
        [Online].
        Available: \urllink{https://www.linuxfoundation.org/blog/blog/linux-runs-all-of-the-worlds-fastest-supercomputers}.

    \bibitem{aws-linux}
        L. Clark,
        ``How Amazon Web Services Uses Linux and Open Source,''
        \textit{The Linux Foundation}, September 8, 2014.
        Accessed February 10, 2024.
        [Online].
        Available: \urllink{https://www.linux.com/news/how-amazon-web-services-uses-linux-and-open-source/}.

    \bibitem{bare-metal}
        M. Salehi, D. Hughes, B. Crispo,
        ``MicroGuard: Securing Bare-Metal Microcontrollers against Code-Reuse Attacks,''
        \textit{2019 IEEE Conference on Dependable and Secure Computing (DSC)},
        Hangzhou, China, IEEE, 2019, pp. 1-8, doi: 10.1109/DSC47296.2019.8937667.
        Accessed February 10, 2024.
        [Online].
        Available: \urllink{https://doi.org/10.1109/DSC47296.2019.8937667}.

    \bibitem{embedded-textbook}
        P. Raghavan, A. Lad, S. Neelakandan,
        \textit{Embedded Linux System Design and Development},
        Boca Raton, FL, Taylor and Francis Group, LLC, 2006.

    \bibitem{rtos-definition}
        A. S. Gillis,
        ``DEFINITION real-time operating system (RTOS),''
        TechTarget
        Accessed February 11, 2024.
        [Online].
        Available: \urllink{https://www.techtarget.com/searchdatacenter/definition/real-time-operating-system}

    \bibitem{intel-hard-soft-real-time}
        Intel,
        ``Real-Time Systems Overview,''
        Intel.
        Accessed February 11, 2024.
        [Online].
        Available: \urllink{https://www.intel.com/content/www/us/en/robotics/real-time-systems.html}

    \bibitem{hard-soft-real-time}
        G. Lipari, L. Palopoli,
        ``Real-Time scheduling: from hard to soft real-time systems,''
        arXiv, 2015.
        Accessed February 11, 2024.
        [Online].
        Available: \urllink{https://doi.org/10.48550/arXiv.1512.01978}

    \bibitem{ubuntu-real-time-part2}
        E. Barbieri,
        ``What is real-time Linux? Part II,''
        \textit{Ubuntu}, February 28, 2023.
        Accessed February 13, 2024.
        [Online].
        Available: \urllink{https://ubuntu.com/blog/what-is-real-time-linux-ii}.

    \bibitem{linux-preemption-models}
        The Linux Foundation,
        ``Preemption Models,''
        \textit{The Linux Foundation}, October 3, 2023.
        Accessed February 13, 2024.
        [Online].
        Available: \href{https://wiki.linuxfoundation.org/realtime/documentation/technical\_basics/preemption\_models}{https://wiki.linuxfoundation.org/realtime/documentation/technical\_basics/preemption \_models}.

    \bibitem{ubuntu-real-time-part3}
        E. Barbieri,
        ``What is real-time Linux? Part III,''
        \textit{Ubuntu}, March 7, 2023.
        Accessed February 13, 2024.
        [Online].
        Available: \urllink{https://ubuntu.com/blog/what-is-real-time-linux-part-iii}.

    \bibitem{rt-linux-riscv}
        J. Markus,
        ``Evaluation of Real-Time Linux on RISC-V processor architecture,''
        Tampere University, March 2022.
        Accessed February 14, 2024.
        [Online].
        Available: \urllink{https://trepo.tuni.fi/handle/10024/138547}

    \bibitem{preempt-rt-survey}
        F. Reghenzani, G. Massari, W. Fornaciari,
        ``The Real-Time Linux Kernel: A Survey on PREEMPT\_RT,''
        New York, NY, USA, Association for Computing Machinery, January 2020.
        Accessed February 14, 2024.
        [Online].
        Available: \urllink{https://doi.org/10.1145/3297714}

    \bibitem{rt-linux-getting-started}
        Michael Barabanov,
        ``Getting Started with RTLinux,''
        \textit{FSM Labs, Inc.}, July 26, 2001.
        Accessed February 14, 2024.
        [Online].
        Available: \urllink{http://cs.uccs.edu/~cchow/pub/rtl/doc/html/GettingStarted/}.

    \bibitem{xenomai-overview}
        Xenomai,
        ``Xenomai 3 Overview,''
        \textit{Xenomai}.
        Accessed February 14, 2024.
        [Online].
        Available: \urllink{https://v3.xenomai.org/overview/}.

    \bibitem{xenomai-overview}
        RTAI,
        ``RTAI Beginner's guide,''
        \textit{RTAI}.
        Accessed February 14, 2024.
        [Online].
        Available: \urllink{https://www.rtai.org/Beginner's-guide.html}.

    \bibitem{vsworks-curiosity}
        VxWorks,
        ``VxWorks Powers NASA JPL's Mars Rover Curiosity,''
        \textit{VxWorks}.
        Accessed February 14, 2024.
        [Online].
        Available: \urllink{https://www.windriver.com/success-stories/nasa-jpl}.

    \bibitem{ecos-overview}
        eCos,
        ``eCos Overview,''
        \textit{eCos}.
        Accessed February 14, 2024.
        [Online].
        Available: \urllink{https://www.ecoscentric.com/ecos/index.shtml}.

    \bibitem{hartos}
        A. B. Lange, K. H. Andersen, U. P. Schultz, A. S. S{\o}rensen,
        ``HartOS - a Hardware Implemented RTOS for Hard Real-time Applications,''
        University of Southern Denmark, 2012.
        Accessed February 14, 2024.
        [Online].
        Available: \urllink{https://doi.org/10.3182/20120523-3-CZ-3015.00041}

\end{thebibliography}
